---
title: "Evaluation Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{evaluation-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

To get things running you have to included the matchingMarketsEvaluation package and some other requirements.
Note that the matchingMarketsEvaluation package is currently based on the function `stabsim3`, which is not yet available in the official package. Please see [github.com/tobiasreischmann/matchingMarkets](https://github.com/tobiasreischmann/matchingMarkets/tree/feature/kita-simulation) for a current development state.

```{r setup}
library(parallel)
library(matchingMarkets)
library(matchingMarketsEvaluation)
```

## Configuration

The package offers evaluation techniques to show how variations of different parameters influence the number of rounds needed for the execution of the decentralized college admission mechanism.
The following code specifies a configuration analysing the mechanism for different values of the cut-off threshold.
This threshold states, how many matchings are tolerated to be different from a full run of the algorithm if we select the results after an earlier round.

```{r configuration}
dimensionxval <- c(0.07,0.05,0.02,0.01,0.005,0.002,0.001)
dimensionxlabels <- percent(dimensionxval, digits = 1)
dimensionx <- "threshold"

elem1 <- list(occupancyrate = 1.2, quota = .6, nStudents = 270, nColleges = 60, 
              areasize = 7, conf.s.prefs = c(3,7,10,10), horizontalscenario = 1)
elem2 <- list(occupancyrate = .8, quota = .6, nStudents = 270, nColleges = 60, 
              areasize = 7, conf.s.prefs = c(3,7,10,10), horizontalscenario = 1)
elem5 <- list(occupancyrate = 1.2, quota = .6, nStudents = 600, nColleges = 200, 
              areasize = 6, conf.s.prefs = c(2,5,6,7), horizontalscenario = 1)
elem3 <- list(occupancyrate = 1.2, quota = .3, nStudents = 270, nColleges = 60, 
              areasize = 7, conf.s.prefs = c(3,7,10,10), horizontalscenario = 1)
elem4 <- list(occupancyrate = .8, quota = .3, nStudents = 270, nColleges = 60, 
              areasize = 7, conf.s.prefs = c(3,7,10,10), horizontalscenario = 1)
elem6 <- list(occupancyrate = .8, quota = .3, nStudents = 600, nColleges = 200, 
              areasize = 6, conf.s.prefs = c(2,5,6,7), horizontalscenario = 1)
elements <- list(elem1, elem2, elem3, elem4, elem5, elem6)
rows <- lapply(elements, function(elem) {
    lapply(dimensionxval, function(x){
      elem[[dimensionx]] <- x
      elem
    })
})
```

## Run the Calculation

The calculation can be run using one simple function.
The results are the needed rounds for all scenarios of the configuration.

```{r gen-data}
data <- calculateScenarios(rows)
```

## Plot the results

Afterwards, the results can be plotted as a line diagram.
```{r plot, fig.width = 7, fig.height = 6}
plotEvaluation(data, elements, "Threshold", dimensionxval)
```
  
